Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-24 Cover_letter_JPM.tex
Answer 2-5

% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO (GSE65858) during candidate selection
In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1 => this is Bonferroni 的結果
Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
The p-values are affected by the sample size, which should be described in the main text. % writing
As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO GSE65858(ok) 
%or even GSE117973? GPL10558	Illumina HumanHT-12 V4.0 expression beadchip; https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE117973
% Progression-free survival (PFS) is "the length of time during and after the treatment of a disease, such as cancer, that a patient lives with the disease but it does not get worse".[1] In oncology, PFS usually refers to situations in which a tumor is present, as demonstrated by laboratory testing, radiologic testing, or clinically. Similarly, "disease-free survival" is when patients have received treatment and are left with no detectable disease.
% disease-specific survival rate: The percentage of people in a study group who have not died from a specific disease in a defined period of time. The time period usually begins at the time of diagnosis of the disease and ends at the time of death from the disease. 
%Patients who died from causes other than the disease being studied are not counted in this measurement.

@@

***...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size

@@

We appreciate the reviewer for the critical comments.
feature selection => includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
# For example, a group of co-regulated genes that are preferable to be taken into consideration in select features.
Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer. These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.

***The RLassoCox\cite{Liu2021} (bioconductor package, available at https://github.com/weiliu123/RLassoCox) trains the RLasso-Cox model based on gene expression profiles, survival information and gene interaction networks.
It is based on the hypothesis that topologically important genes in the gene interaction network tend to have stable expression changes. The RLasso-Cox model uses random walk to evaluate the topological weight of genes, and then highlights topologically important genes to identify survival biomarkers for HNSCC.
dGMMirGraph The KEGG network\cite{Simon2011}\cite{Liu2021}.

%x Bayesian Hyper-LASSO Classification for Feature Selection with Application to HNSCC RNA-seq Data\cite{Jiang2020} -> citing \cite{Li2018d}
RLassoCox\\
We apply Bayesian Logistic Regression with Heavy-tailed Priors\cite{Li2018d} by R package HTLR (available at https://github.com/cran/HTLR) in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
HTLR utilize an Markov chain Monte Carlo (MCMC) method for learning multinomial logistic regression with hyper-LASSO priors. The MCMC algorithm uses Hamiltonian Monte Carlo in a restricted Gibbs sampling framework.

% **** [2021/06/22] by Bayes_survival.R
The results shows
%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
cv.mod.candidate 62 genes are not performed well either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\

@@

%X Bayesian Robit regression method with Hyper-LASSO priors (shortened by BayesHL) for feature selection in high dimensional genomic data with grouping structure.
%We apply BayesHL in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
*** However, the LASSO has been criticized for being biased in gene selection, because it penalizes all the gene coefficients equally\cite{Fan2014}.
% BayesHL is immune to the problem of correlation bias. Other convex and non-convex methods may not be able to identify significant features when there is a high number of correlated features, due to the problem of correlation bias

%coxlogit: https://www.info.ucl.ac.be/~pdupont/pdupont/pdf/MCDM_14.pdf
The Cox proportional hazard regression and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
Here we make use of both tasks by the Coxlogit mixed model.
As such this approach outperforms a Cox proportional hazard model or a logistic regression, each of those models being efficient essentially on their own task\cite{Branders2014}.
*** However, the LASSO has been criticized for being biased in gene selection, because it penalizes all the gene coefficients equally\cite{Fan2014}.
It could be overcame by assigning a consistent weight to each gene, which has been implemented in the adaptive LASSO (APLR)\cite{Algamal2015}\cite{Wu2018}.% was originally proposed to. 
accuracy from 95\% to 97\% :-)

%***  a gene signature with deep learning CNN,
%or http://gepia2.cancer-pku.cn/#index

%cv.mod$glmnetRes$lambda.1se
the most regularized model with cross-validation error within 1 standard deviation of the minimum.

Finally, we use gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).

>>>>

% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO (GSE65858) during candidate selection
In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1 => this is Bonferroni 的結果
Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
The p-values are affected by the sample size, which should be described in the main text. % writing; also affecting the over-fitting during a model training
As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO GSE65858(ok) 
%or even GSE117973? GPL10558	Illumina HumanHT-12 V4.0 expression beadchip; https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE117973
% Progression-free survival (PFS) is "the length of time during and after the treatment of a disease, such as cancer, that a patient lives with the disease but it does not get worse".[1] In oncology, PFS usually refers to situations in which a tumor is present, as demonstrated by laboratory testing, radiologic testing, or clinically. Similarly, "disease-free survival" is when patients have received treatment and are left with no detectable disease.
% disease-specific survival rate: The percentage of people in a study group who have not died from a specific disease in a defined period of time. The time period usually begins at the time of diagnosis of the disease and ends at the time of death from the disease. 
%Patients who died from causes other than the disease being studied are not counted in this measurement.

@@

***...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size, if combine several GSE65858 and with TCGA HNSCC 
An increase of the sample size will decrease overfitting.

@@

We appreciate the reviewer for the critical comments.
 %=> includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
A group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
In the data science literature, feature selection has been usually applied for a group of genes which are contributing as independent variables for building model such as logistic regression. %The dependent variables are the survival data.
%Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer. These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.
Least Absolute Shrinkage and Selection Operation (LASSO):
The feature selection (subsets of gene) could be done by the $L_{1}$-regularized path algorithm in LASSO regression. That is suggested by Branders and his colleagues\cite{Branders2014} applying on those high-dimensional data i.e., twenty thousands of features (genes) and only hundreds of sample size.
LASSO is suitable at picking up a small signal (gene signature) through lots of noise (all protein-coding genes).
% R code by https://www4.stat.ncsu.edu/~post/josh/LASSO_Ridge_Elastic_Net_-_Examples.html

% feature selection by lasso (L1 regularization)
% LASSO, shrinkage coefficients to zero, for selection the features
Cross-validation is perhaps the simplest and most widely used method for select one of models at specific \lambda. % k-fold Cross-validation
As the coefficients of logistic regression are reduced to zero by LASSO, the useless features associated with those coefficients will be omitted.
The important features that contribute much to the model will be selected.
Cross-validation error is calculated to find the optimal value of the regularization rate (i.e., lambda, \lambda). \lambda could control the size of a small amount of bias.
% over-fitting causes problem
During fitting of logistic model, it is necessary to add that small amount of bias for getting a significant drop in the variance to prevent it's over-fitting.  
%(over-fitting is called high-variance)
In case with over-fitting, this trained model will only perfect match every individual cases, while has higher variability to predict what it never see.
Over-fitting could be controlled well by using both LASSO $L_{1}$-regularization and cross validation.

%RLassoCox\\
We utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://\\github.com/weiliu123/RLassoCox) for training the Cox proportional hazard regression and multinomial logistic regression models in gene expression analysis to identify a group of genes that contribute to the survival outcome of HNSCC patient. %and gene interaction networks (The KEGG network\cite{Simon2011}).
% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
% based on gene expression profiles,
The Cox and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
The RLassoCox make use of both tasks for gene-expression based survival analysis.

% medium: https://towardsdatascience.com/regularization-machine-learning-891e9a62c58d

%in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
%It is based on the hypothesis that topologically important genes in the gene interaction network tend to have stable expression changes. The RLasso-Cox model uses random walk to evaluate the topological weight of genes, and then highlights topologically important genes to identify survival biomarkers for HNSCC.
%dGMMirGraph The KEGG network\cite{Simon2011}\cite{Liu2021}.

%HTLR\\
%x Bayesian Hyper-LASSO Classification for Feature Selection with Application to HNSCC RNA-seq Data ***\cite{Jiang2020} -> citing *** \cite{Li2018d} HTLR
%We apply Bayesian Logistic Regression with Heavy-tailed Priors\cite{Li2018d} by R package HTLR (available at https://github.com/cran/HTLR) in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
%HTLR utilize an Markov chain Monte Carlo (MCMC) method for learning multinomial logistic regression with hyper-LASSO priors. The MCMC algorithm uses Hamiltonian Monte Carlo in a restricted Gibbs sampling framework.

%coxlogit\\ 只是 Cox + LR 依照不同比例相加
%https://www.info.ucl.ac.be/~pdupont/pdupont/pdf/MCDM_14.pdf
%The Cox proportional hazard regression and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
%Here we make use of both tasks by the Coxlogit mixed model.
%As such this approach outperforms a Cox proportional hazard model or a logistic regression, each of those models being efficient essentially on their own task\cite{Branders2014}.

% BayesHL (implementation is not found so far)
%X Bayesian Robit regression method with Hyper-LASSO priors (shortened by BayesHL) for feature selection in high dimensional genomic data with grouping structure.
%We apply BayesHL in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
%*** However, the LASSO has been criticized for being biased in gene selection, because it penalizes all the gene coefficients equally\cite{Fan2014}.
%=> Ridge regression 才是
%L2 regularization or Ridge regression. As the parameters "tend to zero" 不是 feature selection (all preserved)
%It could be overcame by assigning a consistent weight to each gene, which has been implemented in the adaptive LASSO (APLR)\cite{Algamal2015}\cite{Wu2018}.% was originally proposed to. 
% only boost accuracy from 95\% to 97\% :-)
% BayesHL is immune to the problem of correlation bias. Other convex and non-convex methods may not be able to identify significant features when there is a high number of correlated features, due to the problem of correlation bias

%***  a gene signature with deep learning CNN, convolutional neural network
%or http://gepia2.cancer-pku.cn/#index

%# Logistics Regression
%# family = binomial 
%# it assumes a linear relationship between link function (***maximum likelihood; likelihood = odds) and independent variables in logit model
%# p(X)(1−p(X)) the odds ratio
%# logit = log(P(x)/(1-P(x))) = β0+β1X
%# l(β0,β1)=p(X)(1−p(X))

% **** [2021/06/22] by Bayes_survival.R
The results shows
%[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
#Calculating Cox p-value...Done [2021/06/22] 19:42
#Performing directed random walk...Done
#Performing cv.glmnet...Done
#code inside: fit.lasso <- glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
the selected features (62 genes) are selected by their (non-zero) coefficients. 
%cv.mod.candidate 62 genes 
However, they are not performed well either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\

@@

% accuracy for the classification in case-control study (or ROC, AUC)
% **** C-index, concordance index for survival data (with censoring)
the Harrell concordance index (C-index) (1996) is the standard performance metric for model assessment in survival analysis with censored data.
%The predictive performances are computed in terms of C-index for the survival prediction.

% Y-axis of the cross-validation error curve (red dotted line) (partial likelihood deviance)
the left vertical line in the plot shows us where the cross-validation error curve hits its minimum. 
The right vertical line shows us the most regularized model with the cross-validation error within 1 standard deviation of the minimum.
% in lambda 1se
%cv.mod$glmnetRes$lambda.1se
the most regularized model with cross-validation error within 1 standard deviation of the minimum.
It selects 14 genes,
according to the \textit{P} value, 4 gene signature: HK1, EZR, RRAGA, and DUSP16.

% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
Finally, we found a gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
